Notebook of learning from ensemble labels

### 2021-06-01 docs/notebook_learn_dl_ensemble.Rmd
Use resume
Modify resume a bit
Modify the tools

```
python hrlcm/fit.py --exp_name unet_single --data_dir 'results/north' --out_dir 'results/dl' --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200
```

@@

  - 0.1 is too large
  - 0.01 and 0.001 works similarly, but 0.001 works slightly better for multiple optimizer.

>>>>

```
python hrlcm/fit.py --exp_name unet_compose_lr --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200
```

```
python hrlcm/fit.py --exp_name unet_compose_lr --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200 --resume 'results/dl/resume/interim.pth' --save_freq 5
```

@@

  - 0.1 is too large
  - 0.01 and 0.001 works similarly, but 0.001 works slightly better for multiple optimizer.
  - Learning rate smaller than 0.0001 might be too small for this case.
